---
title: "LDA for Iris Data"
author: "Gunther"
date: "`r Sys.Date()`"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Iris Data

The Iris Data set in r comes from Edgar Anderson and contains measurments of the sepals and petals of three different species of irises.  These species are setosa, versicolor, and virginica.

Source information is taken from:

Fisher, R. A. (1936) The use of multiple measurements in taxonomic problems. Annals of Eugenics, 7, Part II, 179–188.

The data were collected by Anderson, Edgar (1935). The irises of the Gaspe Peninsula, Bulletin of the American Iris Society, 59, 2–5.

## Measurments taken from the irises.

- The length of the sepal
- The width of the sepal
- The length of the petal
- The width of the petal

```{r iris, echo = TRUE}
summary(iris)
```

## Slide with Plot
The iris data shows some discriminating features so lets try to perform a linear discriminant analysis.  Let's try with two different variables.


```{r, echo=FALSE}
plot(iris, col = iris$Species)
legend("right", legend = levels(iris$Species), col = 1:3, pch = 1:3, title = "Species")
```




## An example of LDA for the Iris Data
You can try out the shiny app [here.](https://gunther-27.shinyapps.io/LDA_Iris_data/)




```{r, echo=FALSE, warning=FALSE}
library(ggplot2)
library(MASS)
input <- list(xcol = 'Sepal.Length', ycol = 'Sepal.Width')

xcol <- input$xcol
ycol <- input$ycol
df <- iris[, c(input$xcol, input$ycol,'Species')]


gg <- ggplot(df, aes_string(x = xcol, y = ycol, color = "Species")) +
    geom_point() +
    labs(x = xcol, y = xcol) +
    theme_minimal()


colnames(df)<- c('xcol','ycol','Species')

lda_mod <- lda(Species ~., data = df)


grid <- expand.grid(xcol = seq(min(df[,1]), max(df[, 1]), length.out = 100),
                    ycol = seq(min(df[, 2]), max(df[, 2]), length.out = 100))


predicted_classes <- predict(lda_mod, newdata = grid)$class


gg <- gg + geom_point(data = grid, aes(x = xcol, y = ycol, color = predicted_classes), alpha = 0.2)

gg <- gg + scale_color_manual(values = c("setosa" = "blue", "versicolor" = "green", "virginica" = "red"),
                              name = "Species")

print(gg)

```